\section{Problem introduction}
This report is written as part of an analysis of a problem at Valcon Group.
The problem analysed is as follows:

\emph{How can the Valcon Group save time and reduce frustration in the IT department by improving the process of new employee registration?}
\\
A more detailed version of the problem statement can be found in appendix \ref{app:problem_statement}.

The problem has been formulated based on an initial meeting with Danni Jensen, who stated that the process should \myquote{identificeres, automatiseres og effektiviseres}.(Appendix \ref{app:danni_initiation})
During the same meeting Danni stated that the most important success criteria for him was that the report could be used to document the existence of the problem.

\section{Methods}
In order to fully understand and analyse the problem we have interviewed several employees of the Valcon Group.
Additionally we have conducted some minor observations of the work processes in the Accounting and IT departments.
We would have liked to supplement this with a questionnaire given to all employees at Valcon Group.
The purpose of the questionnaire would be to get an understanding of the employees perspectives on the process of new employee registration.
However, it was deemed that such a questionnaire would take up too much valuable time from the employees.
\section{Solutions Already Underway}
\input{intro/solutions_already_underway}

\section{Notes}
During the analysis we realized that OMT was an integral part of the problem, and started to analyze them as well.
Our scope got too big, so we limited the amount of gathered knowledge from OMT to a single interview with a recruiter at OMT with a key person in regards to the process. 

We realize that this limits our general understanding of the procress, and thus most of the solutions proposed in regards to OMT are conducted based on limited knowledge, and should be further revised before implemented. 
