Keep 6 pre-installed computers ready for use at OMT and Valcon, for emergencies or very quick recruitments.

\subsubsection{Pros} Would reduce response times to urgent recruitments.
Also useful if an employee's computer breaks, to reduce downtime.

\subsubsection{Cons} Needs a little more managing from IT, as
computers will need to be kept updated and ready.
As not all computers are in use, this creates a small financial overhead.

\subsubsection{Finance} 
This solution has a big initial investment (240.000 DKK) and will not break even unless errors happen.
The money saved comes from employees being able to get back to work quickly after a computer breaks down, or letting new employees start work faster.
Without having numbers on computer errors or quick recruitments, we can not complete the analysis.

\subsubsection{Risks}
Maintaining a buffer of computers could result in the computers getting outdated in case the buffer is too big compared to the amount of new hires.

\subsubsection{Handling risks}
Balancing the amount of computers kept in the buffer will reduce the risk of them getting outdated.

\subsubsection{Conclusion}
Whether this solution should be implemented depends on how many errors happen.
We have not been able to get an estimate of how much time is lost due to computer errors or new employees waiting for computers.
As it would increase work enjoyment in IT, help with errors, and improve response times, we would recommend implementing this even with a small financial loss.