\label{app:cost_benefit_analysis}
These calculations are based on the recruitment and resignation data sheet in appendix \ref{app:recruitment_data}.

\section{Standard process and edge cases}
\begin{itemize}
\item In 2012/13, 118 persons were hired or subcontracted.
\item In 2013/14, 154 persons were hired or subcontracted.
\item In 2014/15, 80 persons have been hired or subcontracted so far.
\end{itemize}
These numbers show how many computers have been made ready by year.
\emph{There is a small increase in the number of computers being readied (30\% in 2013 and (projected) 4\% in 2014).}

\subsubsection{Time spent on computers and data entering}
<<<<<<< HEAD
Peter gave an estimate for how long it took him to set up a computer and enter data into the system, 45 minutes (appendix \ref{app:peter_time_estimation}). (We realize Peter may be wrong about this. We haven't been able to observe the process, but we still think the calculations are useful.)
=======
Peter gave an estimate for how long it took him to set up a computer and enter data into the system, 45 minutes (appendix \quoteref{app:peter}{peter_estimat_setup}). (We realize Peter may be wrong about this. We haven't been able to observe the process, but we still think the calculations are useful.)
>>>>>>> e1a80030bfcb9a1df64d6a7f594a9d11d096aab3

Similarly, Lisbeth estimates that she spends about 15 minutes entering data into the system.

This means, that 118 hours have been used in 2012/13, 154 hours in 2013/14, and 80 hours in 2014/15 so far on computer setup and data entering.

With about 150 hours used every year, even if we save 30 minutes for every recruitment, this is only 75 hours saved every year, so \emph{our proposed solutions need to be inexpensive.}

\subsubsection{Time spent on other things related to recruitment}
<<<<<<< HEAD
Peter uses time on gathering information on telephone and internet connection preferences from the new employees, approx. 10 minutes on average.
This is only on the Danish recruitments, and not on subcontractors.

Furthermore, he uses time on Danish resignations, both subcontractors and hires, approx. 15 minutes on average.
=======
Peter uses time on gathering information on telephone and internet connection preferences from the new employees, appr. 10 minutes on average.
(appendix \quoteref{app:peter}{peter_estimat_contact})
This is only on the Danish recruitments, and not on subcontractors.

Furthermore, he uses time on Danish resignations, both subcontractors and hires, appr. 15 minutes on average.
\todo{Where do we know this from}
>>>>>>> e1a80030bfcb9a1df64d6a7f594a9d11d096aab3
(We realize Peter may be wrong about these. We haven't been able to observe the process, but we still think the calculations are useful.)

\todo{Write something about Lisbeth spending time on acquiring information in edge cases?}

\subsubsection{Total time spent}
Here follows the total amount of time spent on recruitments and resignations each year (barring edge cases).
\begin{itemize}
\item 2012/13 - 140,5 hours.
\item 2013/14 - 186,5 hours.
\item 2014/15 - 95 hours so far. (Half the year has passed, so a reasonable estimate is that 190 hours will be used in total.)
\end{itemize}

As long as there are few edge cases, \emph{the time spent is a small problem.}

\subsubsection{Edge cases}
We haven't been able to get any numbers on the amount of edge cases in the process.

This is problematic, as our main focus is documenting that there is a problem, and the amount of time used without edge cases is small.

And even when edge cases happen, as the process doesn't change, \emph{the time spent doesn't increase, only the amount of frustration in the IT department.}

\subsubsection{Benefits to improving the process}
There are some benefits to changing the recruitment setup process.

Currently, IT and accounting are both frustrated by the process.
By improving the process, the work enjoyment could improve.

Finally, improving the process can speed up response times on support and recruitment from IT and on recruitment in accounting.

\subsubsection{Conclusion of process analysis}
There is little financial gain in changing the recruitment setup process.

The benefits, however, are important and in line with the Valcon's employee values.

So the solutions we propose must be without or with very little cost.

\section{Cost/benefit of solutions}
In this section, we look at the costs of each of our proposed solutions and write a few benefits.
We will not look at the new HR system, as Valcon is already working on it and we do not know enough about the system to correctly estimate costs and benefits. \todo{maybe remove}
To see a description of the solutions, see appendix \ref{app:solution_propositions}

\subsubsection{Software that does it all}
\begin{itemize}
\item \emph{Costs} - Very high. (\textgreater 1,000,000 DKK, drawing on comparable IT solutions in other companies.)
\item \emph{Benefits} - Accounting and IT would be happy, as all data would have to only be entered once. But consultants would be less so, as their work would be slowed down by data entering and a heavy program. (Lower income.)
\item \emph{Conclusion} - This investment would never break even.
\end{itemize}

\subsubsection{Template for recruitment}
\begin{itemize}
\item \emph{Costs} - Three hours for creating the template, an hour every six months to keep it up to date. (500 * 3 = 1500 DKK initially, 500 * 2 = 1000 DKK annually. (Assuming 500 DKK/hour for the employee making and maintaining the template.))
\item \emph{Benefits} - Lisbeth saves time, as data isn't missing, but Hanne and Jytte spend a little more time gathering the information. All three save time as less communication between them is needed. (Lisbeth saves appr. 10 minutes per recruitment, Hanne goes even, Jytte goes even.) (Minutes saved * number of recruitals annually / 60 = hours saved annually = 10 * 180 / 60 = 30 hours saved annually = 9000 DKK saved annually (assuming 300 DKK/hour))
\item \emph{Conclusion} - This investment would break even in the first year, even saving 6500 DKK, and would save 8000 DKK annually afterwards.
\end{itemize}

\subsubsection{Change of attitude toward IT}
\begin{itemize}
\item \emph{Costs} - (Example:) A small, internal campaign to change company attitude might cost appr. 20,000 DKK (Two days work for a designer, printing posters, sending emails, lost time for consultants).
\item \emph{Benefits} - Better communication with IT. We cannot see any financial gain. Would reduce frustration in IT and make IT feel more appreciated.
\item \emph{Conclusion} - Won't break even, but the non-financial benefits are important.
\end{itemize}

\subsubsection{Buffer of ready computers}
\begin{itemize}
	\item \emph{Costs} - 240,000 DKK initially (20,000 DKK * 12 computers). Appr. 1,200 DKK annually for maintenance (8 hours work for a student-helper, 150 DKK per hour pay.)
	\item \emph{Benefits} - Shorter response times from IT, less frustration in IT. Time saved in IT as the computers can be created at the same time. 96 hours saved by student helpers annually = 14,400 DKK saved annually. In cases where a quickly hired employee would not normally be able to start work, because of a delay in getting them a computer, having a buffer can potentially save a lot of money.
	\item \emph{Conclusion} - Will break even after less than 18 years, potentially faster if there are a couple of cases of lost workdays per year. Less frustration in IT and better response times make it worth it.
\end{itemize}

\subsubsection{Increase IT staff size}
\begin{itemize}
	\item \emph{Costs} - Appr. 1,000,000 DKK annually. (Full time employee + management and resource costs.)
	\item \emph{Benefits} - Less frustration in IT. IT would be able to handle a higher workload generally, not just with regards to the process of new employee registration.
	\item \emph{Conclusion} - This is a very expensive solution to the problem. 
\end{itemize}

\subsubsection{New HR-system}
\begin{itemize}
	\item \emph{Costs} - Because the Valcon Group is already looking into a new HR-system it doesn't seem necessary to look at the costs.
	\item \emph{Benefits} - Assuming that the Recruitment, Accounting and IT departments would all be able to access shared information within the new system a total of approx. 60 minutes can be saved per hire across departments. With about 150 new hires per year, a total of 150 hours can be saved. Assuming an average cost of 500 DKK per work hour this is equivalent to 75,000 DKK.\todo{Sources app:<name>\_time\_estimation}
	\item \emph{Conclusion} - Even though the focus of a new HR-system isn't solely the recruitment process, it would also save a considerable amount of money with regards to the recruitment process.
\end{itemize}

\subsubsection{Help-program for finding initials and reading templates}
\begin{itemize}
	\item \emph{Costs} - Writing the program and maintaining it will cost a programmer 5 days initially, and then 1-2 days annually. (12000 DKK initially, then 4800 DKK annually, assuming 300 DKK / hour.)
	\item \emph{Benefits} - Less time spent on entering data, less errors, less frustration for IT. (5 minutes * 156 recruitments / 60 * 300 DKK /hour = 3900 saved annually)
	\item \emph{Conclusion} - This won't break even. Should only be implemented to make IT employees happier (which might be worth it).
\end{itemize}

\subsubsection{Other small improvements}
These are described in detail in appendix \ref{app:solution_propositions}.
\begin{itemize}
	\item \emph{Costs} - These are all free or have very low costs (below 500 DKK over 5 years)
	\item \emph{Benefits} - The benefits are mainly time saved for IT and accounting, except in the case of the mail from OMT, which would help reduce frustration.
	\item \emph{Conclusion} - All three of these save a little money or increase work enjoyment slightly for IT and/or accounting.
\end{itemize}