\section{Premise}

\subsection{Background}
In Valcon, the process of registering new employees is characterized by loose organization. This is a problem, as the company is growing quickly and many employees are recruited, and specialists are recruited for short periods of time. We have been asked to research this process and explore possible solutions, and finally to write a business case explaining the benefits and drawbacks of different solutions.

\subsection{Assignment and Objective}
The objective of the project is to research the process of registering new employees. HR departments in both OMT and Valcon collect information on the new employee and send this to either an accountant or the IT department, depending on what they need done first. This creates an unnecessary need for communication between the IT department and the accountant, which might be avoided if the process was standardized. The accountant enters financial and personal information into a system (QHR), which the IT department then uses to send a computer, setup internet connection and phone accounts, and enter the employee into the central system (AD). To further understand the current situation, the project group will conduct an ethnographic analysis of the process, in an attempt to discover parts of the process that could be effectivised, and look at ways to do so.

\subsection{Financial framework}
There will be no money involved in the project.
The resulting report of the project may be used freely by Valcon.

\subsection{Critical factors}
\textbf{Success factors:}
The solutions proposed should reduce the time, complexity and effort it takes to enter a new employee into the system.
The Business Case provided by the group must, regardless of the solutions proposed, be useable as documentation for the existence of the problem.
The solution proposed must still make use of the Active Directory which Valcon uses for managing their IT structure.
\textbf{Critical preconditions:}
We need to be able to get the time needed from the resources mentioned below.

\section{Organization}
\subsection{Project organization}
The project organization consists of two groups. The project group at ITU consists of Michael Frikke Madsen, Jonas Kastberg Hinrichsen, Martin Juul Petersen, Jakob Ambeck Vase, and Jakob Merrild. They report to Danni Jensen at Valcon.

\subsection{Resources}
The time of the project group.
3 meetings (with a 4th optional one) with Danni Jensen of appr. 1 hour each.
One or two interviews with each key employee in the process (Lisbeth, Peter, Mathias, HR) of appr. 30 min. each.
Open doors, for observing the work practises involved in the process.

\subsection{Stakeholders}
Danni Jensen
Lisbeth Justesen
The IT department of Valcon
HR departments of OMT and Valcon

\subsection{Agreements}
The following agreements were made:
The project group can conduct observations of public areas at Valcon without prior notice.
In order to conduct interviews with and observations of individuals, an agreement must be made with Danni Jensen, who must authorize the project group to initiate contact with the person to be interviewed. 
After the initial contact has been made, the project group is free to contact the person directly in order to make an appointment.

\section{Method}
\subsection{Overall Approach}
The overall approach to the project will be using the MUST method. The MUST method consists of the following four phases:
Initiation phase, where we agree on the problem and a contract
In-Line analysis, where the project group will align the project’s goals with the company’s IT and business strategy
In-depth analysis, where the project group will observe and document the relevant work practices
Innovation phase, where solutions will be investigated and optionally presented

\subsection{Plan}
\begin{itemize}
\item[13/10] - End of In-Line phase.
\item[15/10] - Meeting after In-Line and before In-Depth phases.
\item[10/11] - End of In-Depth phase.
\item[14/11] - Meeting after In-Depth and before Innovation phases.
\item[4/12] - End of Innovation phase
\item[Before] 17/12 - Delivery of Business Case
\item[??] - Optional meeting after Innovation phase.
\end{itemize}

\subsection{Signatures}